Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-02-28 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
28.02

>>>>

	A more general relationship can be obtained by applying multiple linear regression instead of linear regression. The clusters in Figure \ref{fig: Correlations} are close to parallel, suggesting that a plane would combine all the data points. The Reynolds number and flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figure \ref{fig: Correlations_surface}.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Di_Re_F.png}
			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
			\label{fig: Correlations_Di_Re_F}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_Re_F.png}
			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
			\label{fig: Correlations_Gamma_Re_F}
		\end{subfigure}
		\caption{Parameter estimation results}
		\label{fig: Correlations_surface}
	\end{figure}

### 2024-02-28 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
28.02

Laboratory experiments were conducted under various conditions to validate the model's effectiveness. The model parameters, such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data. The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the axial diffusion coefficient, had a low impact on the model's output.

The Reynolds number and Hildebrand solubility parameter were used to analyse the obtained parameters further. The linear correlations between parameters and the Reynolds numbers are presented. $D_i^R$ coefficient decreases with the Reynolds number due to higher fluids density and the corresponding mass transfer resistance, while $\Upsilon$ increases due to increased Hildebrand parameter. It should be noted that outside of the confidence region, the parameters can become negative, which might reverse the direction of the mass transfer.

The presented model might be used as a first approximation and for generating first estimates of the parameters for data correlation. The presented model can be further used with presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes such as techno-economic analysis, optimal design of experiments, or yield maximisation.

>>>>

Laboratory experiments were conducted under various conditions to validate the model. The model parameters, such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data. The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the axial diffusion coefficient, had a low impact on the model's output. The identification of the low impact parameters lead to model reduction

The Reynolds number and Hildebrand solubility parameter were used to analyse the obtained parameters further. The linear correlations between parameters and the Reynolds numbers are presented. $D_i^R$ coefficient decreases with the Reynolds number due to higher fluids density and the corresponding mass transfer resistance, while $\Upsilon$ increases due to increased Hildebrand parameter. It should be noted that outside of the confidence region, the parameters can become negative, which might reverse the direction of the mass transfer and leads to unfeasible solution.

The presented model can be further used with presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes such as yield maximisation, techno-economic analysis, or optimal design of experiments.
